Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-04-29 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
More comments.

  %MRS11: Introduction should not really give the answer so far.
  %Introduction should describe the questions that will be asked, but
  %not answer them.  That's not what is expected in an intro, it may confuse people (answers should be in the abstract).
  %MRS11: this next paragraph could use tweaks/cutting the most, but review the previous paragraphs as well.
  %MRS11: you can think about putting some of these results into conclusion, though - it reads well now, but might be benefited from reemphasizing results if it's currently missing any of this.
  %BJC2: slight tweaks and removed conclusions from following paragraph. Also went back through previous
  % paragraphs to look for conclusions.

@@

  %MRS10: A thought going through this - a diagram with a picture of
  %the molecule pointing to features that promote certain behavior
  %would be interesting here.  I would suggest waiting until we get
  %reviews back, though.  You should get this submitted.

@@

  Despite relatively good predictions of the MD MSD, qualitative mismatch
  between simulated MSDDM and MD trajectories suggest that the MSDDM may be
  getting the right answers for the wrong reasons. We plotted typical
  realizations of the MSDDM for each solute and compared them to MD in
  Figure~\ref{fig:msddm_eyetest}. There is little evidence of trapping behavior
  or large hops. There are two reasons for this behavior. First, the width of
  hop length distributions are much smaller than those of the AD model. Closer
  examination of the characteristic MD trajectories shown in
  Figure~\ref{fig:solute_trajectories} reveal that hops tend to be an
  accumulation of a series of hops in the same direction. All of the hops in
  the MSDDM are negatively correlated which prevents this from happening. The
  second reason is a consequence of using a single hop length distribution for
  transitions. This was necessary because we could not collect enough data to
  fit all of the possible transition distributions and because we could not
  %MRS10: my feeling is (to keep in the back of the mind) that we may be able to add some sort of 
  %prior to fit the transition distributions. Lots of distributions can be fit with low amounts of data
  %if one makes enough assumptions about what the functional form of the distribution is. And we could
  %presumably come up with something reasonable. But that's for another time. 
  correlate emissions coming from different hop distributions. Many
  transitions occur between two trapped states where the transitional hops are
  actually very small. Our model ignores this physical restriction which can
  cause the solute to drift rather than stay trapped.

>>>>

@@

@@

  Despite relatively good predictions of the MD MSD, qualitative mismatch
  between simulated MSDDM and MD trajectories suggest that the MSDDM may be
  getting the right answers for the wrong reasons. We plotted typical
  realizations of the MSDDM for each solute and compared them to MD in
  Figure~\ref{fig:msddm_eyetest}. There is little evidence of trapping behavior
  or large hops. There are two reasons for this behavior. First, the width of
  hop length distributions are much smaller than those of the AD model. Closer
  examination of the characteristic MD trajectories shown in
  Figure~\ref{fig:solute_trajectories} reveal that hops tend to be an
  accumulation of a series of hops in the same direction. All of the hops in
  the MSDDM are negatively correlated which prevents this from happening. The
  second reason is a consequence of using a single hop length distribution for
  transitions. This was necessary because we could not collect enough data to
  fit all of the possible transition distributions and because we could not
  correlate emissions coming from different hop distributions. Many
  transitions occur between two trapped states where the transitional hops are
  actually very small. Our model ignores this physical restriction which can
  cause the solute to drift rather than stay trapped.
